---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# arastocat
**ˋarastocatˋ provides tools to spatially and temporally aggregate raster climate data in NetCDF and bin format.** Many appications that involve climate data require these averaged for defined spatial units and with a specific time interval. For spatial units provided with a shape file ˋarastocatˋ extracts time series of area weighted average values for each spatial unit. The workflow further offers the option to temporally aggregate the timeseries on a 'hourly', 'daily', 'monthly', or 'yearly' timestep. To enable the processing of the data in a modern R programming workflow in the ˋtidyverseˋ the output is given in a tidy tibble. For the use of the aggregsted climate data with the **SWAT** model ˋarastocatˋ gives the option to write the data in the appropriate format.

## Installation

You can install aRastoCAT from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("chrisschuerz/aRastoCAT", dependencies = TRUE)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
